VM-Centric Deduplication with Fault Isolation for Snapshot Backup in the Cloud

### 2014-01-24 snapshot_system/paper_eval.tex
deleted old main.pdf, adjusted failures to 10 for figures

\end{figure}
}
\begin{table}
  \centering
    \footnotesize
    \tabcolsep=0.11cm
    \pgfplotstabletypeset[
        columns={NodesFailed,VO100,VC100,VO1000,VC1000},
        columns/NodesFailed/.style={
            column name={\multirow{3}{*}{Failures ($d$)}}
        },
        columns/VO100/.style={
            column name={
                \multicolumn{4}{c|}{VM Snapshot Availability(\%)}\\&
                \multicolumn{2}{c|}{$p=100$}&\multicolumn{2}{c|}{$p=1000$}\\&
            VO},
            fixed, precision=6
        },
        columns/VC100/.style={
            column name={VC},
            fixed, precision=6},
        columns/VO1000/.style={
            column name={VO},
            fixed, precision=6},
        columns/VC1000/.style={
            column name={VC},
            fixed, precision=6},
        every head row/.style={
            before row={\hline},
            after row={\hline},
        },
        every last row/.style={after row=\hline},
        column type/.add={}{|},
        every first column/.style={column type/.add={|}{}},
        %the below rows can be used to extract rows 3,5,10,20 from rows 0-40
        %skip rows between index={0}{3},
        %skip rows between index={4}{5},
        %skip rows between index={6}{10},
        %skip rows between index={11}{20},
        %skip rows between index={21}{41}
    ]{figures/availability_table.txt}
    \caption{Availability of VM snapshots for VO and VC.}
    \label{tab:vm-availability}
\end{table}

\begin{figure}[htbp]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                        width=\linewidth,
                        height=0.6\linewidth,
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
                xmin=0,
                xmax=20,
		%extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot+[dashed] table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
                \legend{
                    VO,
                    $r_c=4$,
                    $r_c=5$,
                    $r_c=6$,
                    $r_c=9$
                }
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM snapshots in VC with different PDS replication degrees}
  \label{fig:pds-replication}
\end{figure}

>>>>

\end{figure}
}
\begin{table}
  \centering
    \footnotesize
    \tabcolsep=0.11cm
    \pgfplotstabletypeset[
        comment chars=!,
        columns={NodesFailed,VO100,VC100,VO1000,VC1000},
        columns/NodesFailed/.style={
            column name={\multirow{3}{*}{Failures ($d$)}}
        },
        columns/VO100/.style={
            column name={
                \multicolumn{4}{c|}{VM Snapshot Availability(\%)}\\&
                \multicolumn{2}{c|}{$p=100$}&\multicolumn{2}{c|}{$p=1000$}\\&
            VO},
            fixed, precision=6
        },
        columns/VC100/.style={
            column name={VC},
            fixed, precision=6},
        columns/VO1000/.style={
            column name={VO},
            fixed, precision=6},
        columns/VC1000/.style={
            column name={VC},
            fixed, precision=6},
        every head row/.style={
            before row={\hline},
            after row={\hline},
        },
        every last row/.style={after row=\hline},
        column type/.add={}{|},
        every first column/.style={column type/.add={|}{}},
        %the below rows can be used to extract rows 3,5,10,20 from rows 0-40
        %skip rows between index={0}{3},
        %skip rows between index={4}{5},
        %skip rows between index={6}{10},
        %skip rows between index={11}{20},
        %skip rows between index={21}{41}
    ]{figures/availability_table.txt}
    \caption{Availability of VM snapshots for VO and VC.}
    \label{tab:vm-availability}
\end{table}

\begin{figure}[htb]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                        width=\linewidth,
                        height=0.6\linewidth,
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
                xmin=0,
                xmax=10,
		%extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot+[dashed] table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
                \legend{
                    VO,
                    $r_c=4$,
                    $r_c=5$,
                    $r_c=6$,
                    $r_c=9$
                }
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM snapshots in VC with different PDS replication degrees}
  \label{fig:pds-replication}
\end{figure}

\begin{figure}[htb]
  \centering
	\begin{tikzpicture}
		\begin{axis}[
                        width=\linewidth,
                        height=0.6\linewidth,
		%title={PDS Replication affect on availability},
		xlabel={Failed storage nodes},
		ylabel={VM Snapshot Availability (\%)},
                xmin=0,
                xmax=20,
		%extra y ticks={99.9}, %if important numbers are missing
                mark options=solid,
                legend style={
                    cells={anchor=west}, %legend entry alignment
                    legend pos=south west %legend position
                },
                reverse legend,
		]
                \addplot+[dashed] table[x=NodesFailed,y=VO]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC1]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC2]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC3]{figures/node_failures_100.txt};
                \addplot table[x=NodesFailed,y=VC4]{figures/node_failures_100.txt};
                \legend{
                    VO,
                    $r_c=4$,
                    $r_c=5$,
                    $r_c=6$,
                    $r_c=9$
                }
		\end{axis}
	\end{tikzpicture}
  \caption{Availability of VM snapshots in VC with different PDS replication degrees \todo{decide which one}}
  \label{fig:pds-replication-old}
\end{figure}
